Subset occurrence data to IUCN Tropical Andes Lowland and Montane Forest

### 2023-09-27 code/L1/L1_TropicalAndes_subset_occ_forest.Rmd
add genera count and save raster file

```{r}
print("The number of plant records is")
nrow(plant_occ_forest)
print("The number of plant species is")
length(unique(plant_occ_forest$species))
print("The number of plant families is")
length(unique(plant_occ_forest$family))
```

```{r}
print("The number of frugivore records is")
nrow(frugivore_occ_forest)
print("The number of frugivore species is")
length(unique(frugivore_occ_forest$species))
print("The number of frugivore families is")
length(unique(frugivore_occ_forest$family))
```

@@

# Write data to csv
```{r}
# subset plant occ, subset frugivore occ, plant species list, frugivore species list
write.csv(plant_occ_forest, file = file.path(output_path,"TropicalAndes_plant_occ_forest.csv"))
write.csv(frugivore_occ_forest, file = file.path(output_path,"TropicalAndes_frugivore_occ_forest.csv"))
write.csv(TropicalAndes_plant_Forest_SpeciesList, file = file.path(output_path,"TropicalAndes_plant_Forest_SpeciesList.csv"))
write.csv(TropicalAndes_frugivore_Forest_SpeciesList, file = file.path(output_path,"TropicalAndes_frugivore_Forest_SpeciesList.csv"))
```

>>>>

```{r}
print("The number of plant records is")
nrow(plant_occ_forest)
print("The number of plant species is")
length(unique(plant_occ_forest$species))
print("The number of plant genera is")
length(unique(plant_occ_forest$genus))
print("The number of plant families is")
length(unique(plant_occ_forest$family))
```

```{r}
print("The number of frugivore records is")
nrow(frugivore_occ_forest)
print("The number of frugivore species is")
length(unique(frugivore_occ_forest$species))
print("The number of frugivore genera is")
length(unique(frugivore_occ_forest$genus))
print("The number of frugivore families is")
length(unique(frugivore_occ_forest$family))
```

@@

# Write data to csv
```{r}
# subset plant occ, subset frugivore occ, plant species list, frugivore species list
write.csv(plant_occ_forest, file = file.path(output_path,"TropicalAndes_plant_occ_forest.csv"))
write.csv(frugivore_occ_forest, file = file.path(output_path,"TropicalAndes_frugivore_occ_forest.csv"))
write.csv(TropicalAndes_plant_Forest_SpeciesList, file = file.path(output_path,"TropicalAndes_plant_Forest_SpeciesList.csv"))
write.csv(TropicalAndes_frugivore_Forest_SpeciesList, file = file.path(output_path,"TropicalAndes_frugivore_Forest_SpeciesList.csv"))
writeRaster(TropicalAndes_IUCNHabitat_Forest0.3,file.path(output_path, "TropicalAndes_IUCNHabitat_Forest0.3.tif"), overwrite = TRUE)
```
